Embracing the Laws of Physics: \\ Three Reversible Models of Computation

### 2018-06-14 survey/survey.tex
bits in conclusion

CS abstractions are based on ``old'' physics

computer applications are more and more ``physical''

physical principles such as conservation of information should be part
of our foundational abstractions

>>>>

The entire edifice of computer science including its mainstream models
of computations, programming languages, and logics is founded on
\emph{classical physics.} While much of the world phenomena can be
approximated with classical physics, we are reaching a revolutionary
period of quantum technology that challenges many of the classical
assumptions. It remains to be seen how computer science will adapt to
this quantum revolution but we believe that additional physical
principles inspired by quantum mechanics will have to be embraced in
our computational thinking. This paper focused on one such principle
--- \emph{conservation of information} --- and explored some of its
exciting implications to the field of computer science.
